\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{lipsum}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{titlesec}

% Setting the margins for the rustic look
\geometry{top=1in, bottom=1in, left=1.2in, right=1.2in}

% Font settings for a rustic style
\setmainfont{Times New Roman}
\renewcommand{\baselinestretch}{1.5}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textit{A Letter from the Past}}
\fancyhead[R]{\textit{Year of Our Lord 2023}}
\fancyfoot[C]{\thepage}

% Title format
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    \textbf{A Cautionary Tale from the Realm of Speculation}
\end{center}

\noindent Thirteen years ago, we launched \textit{Mann vs. Machine}, a chilling cautionary tale where an artificial consciousness tried to take all our jobs. You didn't know it back then, but that was actually a literary device called "speculative" fiction, where writers (us) accurately predict the future (the present), but then hide it so as not to cause widespread panic.\\

\noindent In an effort to keep panic levels low, and apropos of nothing, we'd like to tell you a story: Once upon a time, a Mann vs. Machine mode in a video game was getting a much-needed update. And so a brave blog post writer (us again) asked the community to submit Mann vs. Machine maps and missions in time for that update. (For the sake of this panic-reducing speculative fantasy, let's put the fictional deadline at Wednesday, August 27th).\\

\noindent If that was the entire story, you'd already be at a low panic level but vaguely concerned about a looming dystopian future (mission accomplished). But as is traditional in the genre of speculative blog fiction, there's more! The king of the fictional land where this all happened (ancient Greece), decreed on stone tablets that even though the update was dropping right around the ancient Greek candy-harvest festival of Halloween, the maps did not need to all be Halloween-themed (first tablet) and in fact shouldn't be (second tablet).\\

\noindent "Though some of them COULD be," the king carved into a third tablet, held in the stone hands of a statue... of PRIMATE GEORGE WASHINGTON? No! It's just regular George Washington in a dystopian future past where our sculptors are NOT AS GOOD AS IN ANCIENT GREECE! What an ending! (The end.)\\

\noindent Is this tale a simple flight of gripping, well-written fancy? (No.) Or a chilling glimpse into a future that could arrive as soon as, again, Wednesday, August 27th with a second part arriving right before Halloween? (Yes, see paragraph one.)

\end{document}