\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% Define custom colors
\definecolor{darkblue}{RGB}{0, 0, 139}
\definecolor{gray}{RGB}{128, 128, 128}

% Set title format
\titleformat{\section}{\color{darkblue}\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\color{darkblue}\bfseries}{}{0em}{}

\begin{document}

\pagestyle{empty} % Remove page numbering

\begin{center}
    {\LARGE \textbf{Dominic Dariano}} \\
    \href{mailto:dominicdariano@gmail.com}{dominicdariano@gmail.com} | 9168356366 | Elk Grove, California
\end{center}

\section*{Education}
\textbf{Sacramento State College}, Sacramento, CA \\
BS Computer Science, GPA: 3.6 \hfill January 2023 -- December 2025 \\

\textbf{Cosumnes River College}, Sacramento, CA \\
General Education, Lower division coursework for computer science, GPA: 3.6 \hfill Aug 2021 -- Dec 2022 \\

\textbf{Laguna Creek High School}, Elk Grove, CA \\
High School Diploma, GPA: 4.0 \hfill Aug 2017 -- May 2021 \\

\section*{Experience}
\textbf{Forte (Formerly AVI Systems)}, Pleasanton, CA \\
Installation Technician \hfill Nov 2024 -- Present \\
\begin{itemize}[left=0pt]
    \item Installed audiovisual equipment, such as displays, cameras, speakers, and related systems at various client sites across the bay area.
    \item Troubleshot various computer related issues in the office.
    \item Assisted with warehouse operations: received and organized incoming equipment, fulfilled pick requests, and maintained inventory.
    \item Gained hands-on experience in cable management, safe practices for warehouse and construction sites, and the installation of a wide range of AV hardware.
    \item Gained experience working in a corporate office environment within a large-scale organization.
    \item Used hand and power equipment for hoisting, measuring, testing, and drilling of various types of installations.
\end{itemize}

\textbf{Regal Cinemas}, Sacramento, CA \\
Floor Staff \hfill Jun 2023 -- Nov 2024 \\
\begin{itemize}[left=0pt]
    \item Worked a variety of positions at the theater including: concessions, greeting guests, cleaning theaters, or working in the kitchen.
    \item Learned how to provide excellent customer service and resolve customer complaints.
    \item Became comfortable working and communicating with new coworkers due to the large staff.
    \item Operated point-of-sale systems for accurate ticket and concession sales.
    \item Provided exceptional customer service to enhance guest experiences at the theater.
    \item Maintained cleanliness and organization of theaters and common areas.
    \item Collaborated with team members to ensure efficient operation during peak times.
\end{itemize}

\textbf{Elk Grove Unified School District}, Elk Grove, CA \\
Substitute Food Nutrition Service Worker \hfill Nov 2022 -- Jan 2023 \\
\begin{itemize}[left=0pt]
    \item Worked in school cafeterias preparing food, serving food to students, and cleaning up messes.
    \item Displayed proper food safety behaviors.
    \item Developed flexibility and quick learning due to this position being a substitute.
    \item Displayed strong communication skills in order to work with new set of co-workers oftentimes each shift.
\end{itemize}

\textbf{Cosumnes River College}, Sacramento, CA \\
Library Student Assistant \hfill Aug 2021 -- May 2022 \\
\begin{itemize}[left=0pt]
    \item Assisted patrons with locating library materials and information resources.
    \item Managed circulation desk, checking out and returning library items efficiently.
    \item Organized and shelved books according to classification systems and library standards.
    \item Provided guidance on library services, programs, and events to visitors.
    \item Learned to adapt well to changing conditions due to the library flooding and the district requiring us to verify if people were vaccinated.
\end{itemize}

\section*{Skills}
\begin{itemize}[left=0pt]
    \item Programming Languages: Java, Python, C, C++, SQL
    \item Front end web development
    \item Strong Work Ethic
    \item Adaptability
    \item Great Communication skills
    \item Troubleshooting and diagnosis
    \item Equipment installation
    \item Customer service
    \item Software configuration
\end{itemize}

\section*{Projects}
\textbf{The Celtic Chariot Website} \\
Node.JS, Vercel, PostgreSQL, BetterAuth, Javascript, HTML/CSS \\
An E-Commerce website for the jewelry business "The Celtic Chariot" \\

\textbf{ZomBalls} \\
Java, Networking, TAGE Game engine, JBullet physics simulation \\
A physics-based zombie survival video game \\

\section*{Awards}
\begin{itemize}[left=0pt]
    \item Dean's List \hfill Jan 2023 - Dec 2025
    \item Full IB Diploma \hfill May 2021
\end{itemize}

\end{document}