\documentclass[12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{setspace}
\usepackage{lipsum}

\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0in}

\begin{document}

\begin{center}
    \textbf{\LARGE An Epistle from Yore}\\[1em]
    \textit{\small Thirteen years past, we commenced the tale of Mann vs. Machine, a chilling cautionary narrative wherein an artificial consciousness endeavored to usurp our occupations. You were unaware then, but it served as a literary contrivance known as "speculative" fiction, where scribes (that is, we) accurately prognosticate the future (which is now our present), yet obscure it to avert widespread consternation.}
\end{center}

\vspace{1em}
In a noble pursuit to maintain a modicum of tranquility, and apropos of naught, we feel compelled to share with thee a story: Once upon a time, a mode of Mann vs. Machine within a certain video game was in dire need of an update. Thus, a valiant writer of blog posts (yes, it is us again) beseeched the community to proffer maps and missions for said mode in time for the aforementioned update. (For the sake of this panic-diminishing speculative fantasy, let us assign a fictional deadline of Wednesday, August 27th.)

\vspace{1em}
Were this the entirety of our tale, thou wouldst already find thyself at a low level of trepidation yet vaguely perturbed by the specter of a looming dystopian future (mission accomplished). But as is customary in the realm of speculative blog fiction, more shall be revealed! The sovereign of the fictional dominion where these events transpired (ancient Greece) did decree upon stone tablets that even though the update coincided with the ancient Greek candy-harvest festival of Halloween, the maps need not be exclusively Halloween-themed (first tablet) and, in truth, ought not to be (second tablet).

\vspace{1em}
"Though some of them COULD be," the king chiseled into a third tablet, firmly grasped by the stone hands of a statue... of PRIMATE GEORGE WASHINGTON? Nay! It is but the common George Washington in a dystopian future past where our sculptors are NOT AS SKILLED AS THOSE OF ANCIENT GREECE! What a conclusion! (The end.)

\vspace{1em}
Is this yarn a mere flight of gripping, well-crafted fancy? (No.) Or a disquieting glimpse into a future that could arrive as soon as, yet again, Wednesday, August 27th, with a second installment gracing thy eyes just before Halloween? (Indeed, see the first paragraph.)

\end{document}